outlier_exploration

### 2025-05-07 Kyubin's Edit/KYUBIN_EDIT.qmd
Changed the data wrangling in KYUBIN_EDIT to the new one, incorporating "pp" variable

```{r}
library(readr)
library(tidyverse)
library(janitor)

sleep <- read_csv("data/Sleep_health_and_lifestyle_dataset.csv") %>% 
  clean_names()

glimpse(sleep)

@@

sleep <- sleep %>%
  mutate(
    systolic = as.numeric(systolic),
    diastolic = as.numeric(diastolic),
    MAP = (2 * diastolic + systolic) / 3
  )

sleep <- subset(sleep, select = -c(person_id, systolic, diastolic))

glimpse(sleep)

>>>>

```{r}
library(readr)
library(tidyverse)
library(janitor)
library(dplyr)

sleep <- read_csv("../data/Sleep_health_and_lifestyle_dataset.csv") %>%  
  clean_names()

@@

sleep <- sleep %>%
  mutate(systolic = as.numeric(systolic),
         diastolic = as.numeric(diastolic),
         PP = systolic-diastolic)

sleep <- sleep %>%
  dplyr::select(!c(person_id, systolic, diastolic))
